%!LW recipe=latexmk
\documentclass[11pt,a4paper]{article}
\input\input{../macros.tex}
\title{Learning Notes}
\author{Yingjie Zhu}
\date{\today}


\begin{document}
\maketitle

\section{Theory of Real Variable Function}

\begin{exercise}
    let $A$ and $B$ be measurable set, then $A \cup B$ is also measurable.
\end{exercise}

\begin{proof}
    \begin{align*}
        m^*(T) & \le m^*(T \cap (A \cup B)) + m^*(T \cap (A \cup B)^C) \\
            & \le m^*(T \cap A \cap B) + m^*(T \cap A \cap B^C) + m^*(T \cap A^C \cap B) + m^*(T \cap A^C \cap B^C) \\
            & \le m^*(T \cap A) + m^*(T \cap A^C) \\
            & \le m^*(T)
    \end{align*}
\end{proof}

\begin{exercise}
    let $A$ and $B$ be disjoint measurable sets. then we have
    \[
        m^(A \cup B) = m^(A) + m^(B)
    \]
\end{exercise}

\begin{proof}
    we take the definition on $A$ is measurable:

    \begin{align*}
        m^*(A \cup B) &= m^*((A \cup B) \cap A) + m^*((A \cup B) \cap A^C) \\
        &= m^*(A) + m^*(B)
    \end{align*}
\end{proof}

\begin{exercise}
    let $E_n$ be a sequence of measurable of disjoint sets. then their countable union $E$

    \[
        E = \bigcup_{n=1}^{\infty}E_n
    \]

    is also measurable.
\end{exercise}


\begin{proof}
    we take finite parts of $E$, let 

    \[
        S_k = \bigcup_{n=1}^{k}E_n
    \]

    and $S = E$


    since $S_k$ is measurable, then we have

    \begin{align*}
        m^*(T) \ge m^*(T \cap S_k) + m^*(T \cap S_k^C) \\
        \ge \sum_{n=1}^{k}m^*(T \cap E_n) + m^*(T \cap S_k^C) \\
        \ge \sum_{n=1}^{k}m^*(T \cap E_n) + m^*(T \cap S^C)
    \end{align*}

    take $k \to \infty$, then we have

    \[
        m^*(T) \ge \sum_{n=1}^{\infty}m^*(T \cap E_n) + m^*(T \cap S^C)
    \]
    
    consider the property of outer measure, then we have

    \[
        m^*(T) \ge m^*(T \cap S) + m^*(T \cap S^C)
    \]

    so $S$ is measurable
\end{proof}

\begin{exercise}
    let $E_n$ be a sequence of disjoint measurable sets, then we have

    \[
        m^*(\bigcup_{n=1}^{\infty}E_n) = \sum_{n=1}^{\infty}m^*(E_n)
    \]
\end{exercise}

\begin{proof}
    we will use conclusion from previous exercise. let $S=E$ 
    \[
        m^*(T) \ge \sum_{n=1}^{\infty}m^*(T \cap E_n) + m^*(T \cap S^C)
    \]

    let $T = S$, then we have

    \begin{align*}
        m^*(S) & \ge \sum_{n=1}^{\infty}m^*(E_n) + m^*(\emptyset) \\
        & \ge \sum_{n=1}^{\infty}m^*(E_n)
    \end{align*}

    so we have

    \[
        m^*(S) = \sum_{n=1}^{\infty}m^*(E_n)
    \]
\end{proof}

\begin{exercise}
    let $E_n$ be a sequence of measurable sets, and they don't have to be disjoint. then
    theire countable union is measurable.
\end{exercise}

\begin{proof}
    take  $A_0 = \emptyset$ and 

    \[
        A_{n} = \bigcup_{k=1}^{n}E_n \setminus \bigcup_{k=1}^{n-1}E_n
    \]

    then $A_0, A_1, ..$ is a sequence of disjoint measurable sets.

    and we have

    \[
        E = \bigcup_{n=0}^{\infty}A_n
    \]

    so $E$ is measurable.
\end{proof}

\end{document}










